VISUALIZATION OF THE RIEMANN-LIOUVILLE FRACTIONAL INTEGRAL \\ [3pt] IN ``FCAA'' JOURNAL

### 2019-10-03 fractional/FCAA/Authors Kit (Updated)/FCAA-template-for-authors.tex
started making sense of paper wording

@@

\begin{theorem}
\label{t:reverse}
Let $\widetilde{g}(x)$ and $f(x)$ be known (continuous) invertable real-valued functions. Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.  If $f^{-1}(0) - \widetilde{g}\circ f^{-1}(0) + \widetilde{g}(a')$ exists then there exists a unique 
$C\in\mathbb{R}$ such that 
\begin{equation}
\int_{a'}^{b'} f(x)\,dg(x)~\textrm{and}~\int_{a(y)}^{b(y)} f(x)\,dx, 
\end{equation}
where $g(x) = \widetilde{g}(x) + C$ and $a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$, have the exact same 
geometric meaning.
\end{theorem}

To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$. We can now compute the following:
\begin{itemize}
 \item Compute $a(y)$ using: 
\begin{equation}
a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
\end{equation}
 \item Compute $a = a(0)$.
 \item Compute $C = a - \widetilde{g}(a')$.
 \item Compute $g(x) = \widetilde{g}(x) + C$.
 \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
\end{itemize}
The integrals $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a'}^{b'} f(x)\,dg(x)$ are equivalent (we obtain the same result when they are evaluated). Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ have the exact same geometric meaning. Note, however, that
$\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ do not have the exact same geometric meaning.

@@

\begin{theorem}
If $\tau\in(-\infty,t]$ then $g_t^{\alpha}(\tau)$ is an invertable function. Its inverse is:
\begin{equation}
h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
\end{theorem}
\begin{proof}
The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ if $\tau\in(-\infty,t]$. The inverse now follows trivially.  
\end{proof}

@@

>>>>

\begin{definition}
The Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,dg(x)$ and the Cavalieri integral $\int_{a(y)}^{b(y)}f(x)\,dx$ are said to be geometrically equivalent if the same result is obtained when they are evaluated and $g(a')=a(0)=a$. 
\end{definition}

@@

\begin{theorem}
\label{t:reverse}
Let $\widetilde{g}(x)$ and $f(x)$ be known (continuous) invertable real-valued functions.
The function $\widetilde{g}(x)$ should also be differentiable. Moreover, let $a'\in \mathbb{R}$ and $b'\in \mathbb{R}$.  If $a(y)=f^{-1}(y) - \widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a')$ and $a(0)$ exists then there exists a unique 
$C\in\mathbb{R}$ such that 
\begin{equation}
\int_{a'}^{b'} f(x)\,dg(x)~\textrm{and}~\int_{a(y)}^{b(y)} f(x)\,dx, 
\end{equation}
where $g(x) = \widetilde{g}(x) + C$, are geometrically equivalent.
\end{theorem}

To clarify the above theorem, consider the Riemann-Stieltjes integral $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$. We can now compute the following:
\begin{itemize}
 \item Compute $a(y)$ using: 
\begin{equation}
a(y) = f^{-1}(y)-\widetilde{g}\circ f^{-1}(y) + \widetilde{g}(a'). 
\end{equation}
 \item Compute $a = a(0)$.
 \item Compute $C = a - \widetilde{g}(a')$.
 \item Compute $g(x) = \widetilde{g}(x) + C$.
 \item Compute $b = g(b')$ and $b(y) = a(y) + (b-a)$.
\end{itemize}
Note that $\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)=\int_{a'}^{b'} f(x)\,dg(x)$ due to Theorem xx. Moreover, Moreover, the integrals $\int_{a'}^{b'} f(x)\,d\,g(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are geometrically equivalent. Note, however, that
$\int_{a'}^{b'} f(x)\,d\,\widetilde{g}(x)$ and $\int_{a(y)}^{b(y)}f(x)~dx$ are not geometrically equivalent.

@@

\begin{theorem}
The function $g_t^{\alpha}(\tau)$ is invertable. Its inverse is:
\begin{equation}
h_t^{\alpha}(\tau) = t - \sqrt[\alpha]{t^{\alpha} - \Gamma(\alpha+1)\tau}.
\end{equation}
\end{theorem}
\begin{proof}
The function $g_t^{\alpha}$ is invertable, since $\frac{d g_t^{\alpha}}{d\tau}=\frac{(t-\tau)^{\alpha-1}}{\Gamma(\alpha)} > 0$ for $\tau\in(-\infty,t]$. The inverse now follows trivially.  
\end{proof}

@@

\section{Existing Geometric Interpretation}

\section{Converting into a Cavalieri integral}

\begin{theorem}
Let $a(y)_{t}^{\alpha} = f^{-1}(y) - \widetilde{g}_t^{\alpha}\circ f^{-1}(y) + \widetilde(g)_t^{\alpha}(a')$. If $a(y)_t^{\alpha}$ and $a(0)$ exists then  
the following integrals are equivalent:

\end{theorem}
